\begin{hcarentry}[updated]{ghc-mod --- Happy Haskell Programming}
\report{Kazu Yamamoto}
\status{open source, actively developed}
\makeheader

{\tt ghc-mod} is a backend command to enrich Haskell programming on editors including Emacs and Vim. The ghc-mod package on Hackage includes the {\tt ghc-mod} command and Emacs front-end. 

Emacs front-end provides the following features:

\begin{description}
\item[Completion] You can complete a name of keyword, module, class, function, types, language extensions, etc.

\item[Code template] You can insert a code template according to the position of the cursor. For instance, ``module Foo where'' is inserted in the beginning of a buffer.

\item[Syntax check] Code lines with error messages are automatically highlighted thanks to flymake. You can display the error message of the current line in another window. {\tt hlint} %\cref{hlint} 
can be used instead of GHC to check Haskell syntax. 

\item[Document browsing] You can browse the module document of the current line either locally or on Hackage.

\item[Expression type] You can display the type/information of the expression on the cursor. 
\end{description}

There are two Vim plugins:

\begin{itemize}
\item ghcmod-vim
\item syntastic
\end{itemize}

Here are new features:

\begin{itemize}
\item {\tt ghc-mod} now analyses library dependencies from a cabal file.
\item The ``{\tt check}'' subcommand became faster than before unless Template Haskell is used. 
\item The ``{\tt debug}'' subcommand is provided.
\item The ``{\tt browse}' subcommand displays more information on functions etc if the ``{\tt -d}'' option is specified.
\end{itemize}

\FurtherReading
  \url{http://www.mew.org/~kazu/proj/ghc-mod/en/}
\end{hcarentry}
